Introduction of using AWS instance to run experiments

### 2022-03-09 docs/run_experiments.Rmd
Forgot to change the default final_lr back
Update some scripts

#### Hierachical training

- Train a big model using the whole dataset over the whole area.
- Fine tune (or transfer) the model into 5 sub zones.

@@

@@

For example:
```
python hrlcm/predict.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl
```

>>>>

Experiments indicate using all of them can improve model performance.

#### Loss functions

No luck on using different loss function. The most effective loss function is still the balanced cross entropy loss function.

According to the experiments, balanced cross entropy loss performs well. In summary (based on my knowledge), changing loss function is not an efficient and effective way to increase the model performance in this case. This might because the modeling task here does not have special characteristics that need special loss functions to deal with. For example, some loss functions were created to detect vessel-like objects. Instead, the problems here are mainly the noisy labels and not enough representative features (satellite image bands).

#### Loss weights

According to some experiments, the accuracy of cropland is relatively low. One reason is that the farming condition over Tanzania is complex and thus hard to model. Another reason is the validation of this class has relatively low quality as well. There are limited things we could do for these reasons. But we can let the model to consider more about cropland when training. The strategy can be increasing the loss weight of cropland class. However, the effect is not conclusive.

#### Ensemble training

When training a full model using the whole dataset, the main problem is cropland. One reason is that
cropland highly relies on local climate and cultivating conditions and Tanzania is a large country.

- Train multiple models with subset of labels.

  - Zone 1, 2, 3, 4, 5 (composite learning rate)
  - Zone 1, 2, 3, 4
  - Zone 1, 2, 3, 5
  - Zone 1, 2, 4, 5
  - Zone 1, 3, 4, 5
  - Zone 2, 3, 4, 5

- Ensemble these models by voting, possibly at segment level.

@@

Zone 1, 2, 3, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```
Zone 1, 2, 3, 4
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```
Zone 1, 2, 3, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```
Zone 1, 2, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```
Zone 1, 3, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```
Zone 2, 3, 4, 5
```
python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
```

@@

For example:
```
python hrlcm/predict.py --args_path 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-54-163-146-125.compute-1.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/tanzania/prediction/unet_zone1_12bs_4augs_80epochs
```
